Parameter estimation

### 2023-03-06 SFE-article/Article_Model_Parameters.tex
06.03

\section{Materials and methods} \label{CH: Materials and methods}
%\subfile{Sections/Materials_and_methods}

\subsection{Extraction model} \label{CH: Extraction_model}
\subfile{Sections/Model}

@@

@@

\clearpage

\subsection{Parameter estimation} \label{CH: Parameter_estimation}
\subfile{Sections/Parameter_estimation}

@@

\begin{figure*}[h!]
		\centering
		\includegraphics[trim = 0cm 0cm 0cm 0cm,clip,width=\textwidth]{Figures/Results_estimation/Yield.pdf}	
		\caption{The yield curve vs dataset}
\end{figure*}

\begin{figure*}[h!]
	\centering
	\includegraphics[trim = 0cm 0cm 0cm 0cm,clip,width=\textwidth]{Figures/Results_estimation/Profiles.pdf}	
	\caption{The fluid density based on the Peng-Robinson equation of state}
\end{figure*}

@@

\clearpage \appendix \label{appendix}
\section{Appendix} 
\subsection{Governing equations}
\subfile{Sections/Gouverning_equation_derivation}

\subsection{Bayes theorem} \label{CH: Bayes}
\subfile{Sections/Bayes_Theorem}

>>>>

%\section{Materials and methods} \label{CH: Materials and methods}

\section{$CO_2$ properties} \label{CH: Thermodynamic}
%\subfile{Sections/Thermo}

\clearpage
%\subfile{Sections/Materials_and_methods}

\subsection{Governing equations}
The detail derivation of the governing equation can be found in the appendix (\ref{CH: Gouverning equations}). Let's assume that any properties of the flow are unifrom across any given cross-section of an channel (or any device like an extractor). Such a floww is called quasi-one-dimensional. The variation of the cross-section might be an result of its irregular shape (or partial filling of an extractor).

The quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates is given be equations \ref{EQ: CompressibleEuler}

{\footnotesize
\begin{equation}
\begin{align}
        \cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} &= 0 \\
        \cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial P}{\partial z} \\
        \cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial T}{\partial z} \right)   
    \end{align}    
\end{equation}
\label{EQ: CompressibleEuler}
}

where $\rho_f$ is the density of the fluid, $A_f$ is the function which describe change of the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.

@@

\subsection{Extraction model} \label{CH: Extraction_model}
%\subfile{Sections/Model}

@@

\subsection{Parameter estimation} \label{CH: Parameter_estimation}
%\subfile{Sections/Parameter_estimation}

@@

@@

\clearpage \appendix \label{appendix}
\section{Appendix} 
\subsection{Governing equations}
%\subfile{Sections/Gouverning_equation_derivation}

\subsection{Bayes theorem} \label{CH: Bayes}
%\subfile{Sections/Bayes_Theorem}

### 2023-03-06 SFE-article/Sections/Low_mach_number_expansion.tex
06.03

	As discussed by \citet{Lions2013}, the low Mach number equations are a subset of the fully compressible equations of motion (continuity, momentum and energy). Such a set of equations allow for large variations in gas density but it is consider to be acoustically incompressible. The low Mach number equations are preferred over the full compressible equations for low speed flow problems $\left( M_a = \cfrac{|V|}{\sqrt{ \partial P / \partial \rho }} \ll 1 \right)$ to avoids the need to resolve fast-moving acoustic signals. The equations are derived from the compressible equations based on the perturbation theory. The perturbation theory develops an expression for the desired solution in terms of a formal power series known as a perturbation series in some "small" parameter $\zeta$, that quantifies the deviation from the exactly solvable problem. The leading term in this power series is the solution of the exactly solvable problem, while further terms describe the deviation in the solution, due to the deviation from the initial problem.

	The equations {\color{red}RED} describe the fully compressible equations of motion (respectively the transport of mass, momentum and energy) for quasi-one-dimensional case. We rescale the time variable, considering finally

>>>>

	As discussed by \citet{Lions2013}, the low Mach number equations are a subset of the fully compressible equations of motion (continuity, momentum and energy). Such a set of equations allow for large variations in gas density but it is consider to be acoustically incompressible. The low Mach number equations are preferred over the full compressible equations for low speed flow problems $\left( M_a = \frac{|V|}{\sqrt{ \partial P / \partial \rho }} \ll 1 \right)$ to avoids the need to resolve fast-moving acoustic signals. The equations are derived from the compressible equations based on the perturbation theory. The perturbation theory develops an expression for the desired solution in terms of a formal power series known as a perturbation series in some "small" parameter $\zeta$, that quantifies the deviation from the exactly solvable problem. The leading term in this power series is the solution of the exactly solvable problem, while further terms describe the deviation in the solution, due to the deviation from the initial problem.

	The equations \ref{EQ: CompressibleEuler} describe the fully compressible equations of motion (respectively the transport of mass, momentum and energy) for quasi-one-dimensional case. We rescale the time variable, considering finally

### 2023-03-06 SFE-article/Sections/Model.tex
06.03

		Since the solute is assumed to be a single pseudo-component, there is only one mass balance equation for each phase (Eq. s \ref{Model_fluid} and \ref{Model_solid}). On the other hand, there is only one heat balance (Eq.  \ref{Model_heat}) because the presence of a single pseudo-phase is assumed.

@@

			\subsubsection{Thermodynamic} \label{CH: Thermodynamic}
			%{\color{blue}The Peng-Robinson equation of state is used to describe the thermodynamics of the fluid phase. The thermal properties of the pseudo-homogeneous phase are assumed to vary along the extractor, though always remaining equal to the corresponding mean values between the fluid and solid phase. }

			%In the process model, properties of the supercritical fluid such as the density ${\color{orange}\rho} ({\color{blue}T}(t,z),{\color{red}P}(t))$, the specific heat ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$, the thermal conductivity ${\color{orange}k^T}({\color{blue}T}(t,z),{\color{red}P}(t))$, or the viscosity ${\color{orange}\eta}({\color{blue}T}(t,z),{\color{red}P}(t))$ are calculated based on the local temperatures along the fixed bed and the pressure. The Peng-Robinson equation of state is used to find values of a ${\color{orange}\rho} ({\color{blue}T}(t,z),{\color{red}P}(t))$ and ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$.

			At standard atmospheric pressure and temperature, the $CO_2$ behaves as an ideal gas, and its compressibility factor equals to unity.  However, at high temperature and pressure, the compressibility factor varies from unity, due to real gas effects.  In order to predict this real gas effects, the Peng-Robinson equation of state (P-R EOS) is used to compute properties of $CO_2$. As the density is obtained from the continuity equation,store the P-R EOS can used to evaluate: compressibility, density and specific heat. The properties of the $CO_2$ computed as a function of operating conditions (temperature and pressure) are presented on fig. \ref{fig: SFE_Properties}

			\begin{figure*}[h!]
				\begin{subfigure}[b]{\textwidth}
					\centering
					\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
					\caption{The compressibility factor based on the Peng-Robinson equation of state}
				\end{subfigure}
				\hfill
				\begin{subfigure}[b]{\textwidth}
					\centering
					\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/RHO.pdf}	
					\caption{The fluid density based on the Peng-Robinson equation of state}
				\end{subfigure}
				\hfill
				\begin{subfigure}[b]{\textwidth}
					\centering
					\includegraphics[trim = 2.9cm 7cm 3.cm 7cm,clip,width=\textwidth]{Figures/CP.pdf}	
					\caption{The specific heat of the $CO_2$ based on the Peng-Robinson equation of state}
				\end{subfigure}
				\caption{Properties of $CO_2$ based on the equation of state}
				\label{fig: SFE_Properties}
			\end{figure*}

			\subsubsection{Dependencies} \label{CH: Dependencies}
			%The inter-particle diffusion coefficient ${\color{orange}D^M_e}(\allowbreak{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is calculated from the empirical correlation, as the function of the Reynolds number ${\color{orange}R_e}({\color{blue}T}(t,z),{\color{red}P}(t),\allowbreak{\color{red}F}(t))$ and the Peclet's number ${\color{orange}P_e}({\color{blue}T}(t,z),\allowbreak{\color{red}P}(t),{\color{red}F}(t))$.
			%The values of the internal diffusion ${\color{orange}D_i} ({\color{blue}T}(t,z))$ and the partition coefficient ${\color{orange}k_m} ({\color{blue}T}(t,z))$ come from the laboratory experiments. The expressions and the detailed information of the parameter fitting can be found in the appendix.

			TODO:

			\begin{enumerate}
				\item Viscosity
				\item Thermal conductivity
				\item Internal diffusion
				\item Partition factor
			\end{enumerate}

>>>>

		Since the solute is assumed to be a single pseudo-component, there is only one mass balance equation for each phase (Eq.s \ref{Model_fluid} and \ref{Model_solid}). On the other hand, there is only one heat balance (Eq. \ref{Model_heat}) because the presence of a single pseudo-phase is assumed.

@@

### 2023-03-06 SFE-article/Sections/Model_2.tex
06.03

>>>>

    {\color{blue}The solid-fluid extraction process is assumed to operate in a semi-continuous mode in a cylindrical vessel. In the extractor, essential oils are removed from biomass (for example, carqueja seeds) by supercritical carbon dioxide. As the solvent flows continuously through the bed of porous particles, the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles. Then the solute dissolves and diffuses into the solvent in the pores and eventually into the bulk. The solvent-solute mixture leaves the extractor and undergoes depressurization. The $CO_2$ is released to a gaseous state, and the solute precipitates. In the vapour-liquid separator, the gaseous solvent is vent off while the precipitated product is collected.

		In Figure \ref{fig: SFE_drawing}, an instrumental set-up is presented. The flow rate ($F_{in}$) and the temperature ($T_{in}$) of the solvent entering the extractor are measured and can be adjusted using a pump and a heat exchanger, respectively. Moreover, the extractor's pressure ($P$) is assumed to be measurable and adjustable using a back-pressure regulator valve. In addition, the temperature of the outlet stream $T_{out}$ and the temperature profile of the fixed-bed can be measured. }

	\begin{figure}[h]
		\centering
		\includegraphics[trim = 6cm 7.5cm 8cm 6cm, clip, width=\linewidth]{SFE_PFD.pdf}
		\caption{Process flow diagram for solid-fluid extraction process}
		\label{fig: SFE_drawing}
	\end{figure}
